\documentclass{article}
\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}

\newcommand{\sbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{2}\end{picture}\ }
\pagenumbering{gobble}
\raggedright
\setlength{\tabcolsep}{0in}
\hypersetup{
  colorlinks,
  linkcolor=blue,
  urlcolor=blue
}

\begin{document}

%=== Header ===
{\LARGE \bf Adityaa Saha}\par
\vspace{1mm}
{\small
  Email: \href{mailto:23cs01002@iitbbs.ac.in}{23cs01002@iitbbs.ac.in} \hfill
  GitHub: \href{https://github.com/Adityaa-Saha17}{Adityaa Saha}\par
  LinkedIn: \href{https://www.linkedin.com/in/adityaa-saha-533b02299/}{Adityaa Saha}\par
}

\vspace{3mm}

%=== Objective ===
\noindent
\textbf{Objective} \\
Seeking a summer internship in software development where I can apply my skills in programming, problem‑solving, and learn industry best‑practices.

\vspace{2mm}

%=== Education ===
\noindent
\textbf{Education} \hrulefill

{\bf B.Tech in Computer Science and Engineering}, \emph{IIT Bhubaneswar} \hfill {\it Expected Graduation: April 2027}\\
CGPA: 6.5/10

\vspace{2mm}

%=== Relevant Coursework ===
\noindent
\textbf{Relevant Coursework} \\
\begin{itemize}[noitemsep, left=0pt]
  \item Transducers, Sensors and Measurements
  \item Data Structures \& Algorithms
  \item Database Management Systems
  \item Operating Systems
  \item Computer Networks
  \item Object‑Oriented Programming
\end{itemize}

\vspace{2mm}

%=== Technical Skills ===
\noindent
\textbf{Technical Skills} \\
\begin{tabular}{@{}p{3.2cm} p{12cm}@{}}
  {\sbt} \textbf{Languages:} & C, C++, JavaScript \\
  {\sbt} \textbf{Web \& Tools:} & HTML5, CSS3 \\
  {\sbt} \textbf{Frameworks:} & React, Node.js, Express, Three.js \\
  {\sbt} \textbf{Databases:} & MySQL, MongoDB \\
\end{tabular}

\vspace{2mm}

%=== Projects ===
%=== Projects ===
%=== Projects ===
\noindent
\textbf{Projects} \hrulefill

\begin{itemize}[noitemsep, left=0pt]
  \item {\sbt} \textbf{Social Media App (In Progress)} — 
  \href{https://github.com/Adityaa-Saha17/Social-Media-App}{GitHub Repository} \\
  Building a full-stack social media application using React, Node.js, Express, and MongoDB. 
  Planned features include user authentication, post creation, likes, comments, and a responsive UI.
\end{itemize}


\vspace{2mm}

%=== Positions of Responsibility ===
\noindent
\textbf{Positions of Responsibility} \\
\begin{itemize}[noitemsep, left=0pt]
  \item {\sbt} Member, Dramatics Society.
  \item {\sbt} Volunteer, Annual Cultural Fest Organizing Committee.
\end{itemize}

\vspace{2mm}

%=== Extracurricular Activities ===
\noindent
\textbf{Extracurricular Activities} \\
\begin{itemize}[noitemsep, left=0pt]
  \item {\sbt} Member of Dramatics Society "The Fourth Wall" of IIT BHubaneswar.
  \item {\sbt} Active member of the college football team.
\end{itemize}

\vspace{2mm}

%=== Achievements & Certifications ===
\noindent
\textbf{Achievements \& Certifications} \\
\begin{itemize}[noitemsep, left=0pt]
  \item {\sbt} 6.5 CGPA.
  \item {\sbt} Completed “Introduction to Algorithms” course on Coursera.
\end{itemize}

\vspace{2mm}

%=== Interests ===
\noindent
\textbf{Interests} \\
Full-Stack, Competitive Programming

\end{document}
